Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-02 Paper/methodology.tex
Update paper sections
Add wall model description

\section{Methodology}
\fxnote{Write something about what we're comparing with, the codes we're
using, and how we set up the simulations.}

@@

To maintain consistency with the measured data, the turbulence
intensity (TI) is calculated using the TKE as
\begin{equation}
  \textrm{TI} =
  \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
  \frac{\sqrt{\frac{1}{3}\left( \overline{u'u' + v'v' + w'w'}
      \right)}}{\overline{U}_{horiz}}
\end{equation}
The averaged wind speeds were enforced at the measurement height of
20m, and the applied wind directions were consistent with the
predominant stable direction of 225 degrees southwest.

@@

\subsubsection{\label{sec:wallmodelBC}Lower wall model BC}
\fxnote{Ganesh write this part}\\
What we implemented in terms of the lower boundary condition.

>>>>

\section{Methodology}
%%\fxnote{Write something about what we're comparing with, the codes we're
%%using, and how we set up the simulations.}

@@

To maintain consistency with the measured data, the turbulence
intensity (TI) is calculated using the TKE as
\begin{equation}
  \textrm{TI} =
  \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
  \frac{\sqrt{\frac{1}{3}\left( \overline{u'u'} + \overline{v'v'} + \overline{w'w'}
      \right)}}{\overline{U}_{horiz}}
\end{equation}
The averaged wind speeds were enforced at the measurement height of
20m, and the applied wind directions were consistent with the
predominant stable direction of 225 degrees southwest.

@@

\subsubsection{\label{sec:wallmodelBC}Lower wall model BC}
\fxnote{Ganesh write this part}\\
The sub-filter scale stresses are specified at the terrain boundary following
Moeng~\cite{Moeng1984} as
\begin{align}
 (\tau_{xz})_0 &= \average{\tau_{xz}}_0 \frac{S_1 \average{\widetilde{u}_1} + \average{S_1} (\widetilde{u}_1 - \average{\widetilde{u}_1} ) }{ \average{S_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
 (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{S_1 \average{\widetilde{v}_1} + \average{S_1} (\widetilde{v}_1 - \average{\widetilde{v}_1} ) }{ \average{S_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } \\
  (\tau_{\theta z})_0 &= \average{\tau_{\theta z}}_0 \frac{S_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{S_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{S_1} ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) },
\end{align}
where all quantities with the subscript 1 are values at the first vertical grid
level, $S_1$ is the resolved wind speed at the first grid level and
$\average{f}$ represents the horizontal planar average of $f$. The mean
sub-filter stresses are computed using Monin-Obukhov similarity
law~\cite{Etling1996}. The formulation for the potential temperature flux could
potentially experience a singularity when the mean resolved potential
temperature at the first grid level $\average{\widetilde{\theta}_1}$ crosses the
reference temperature $\theta_{\circ}$. Hence the model for the sub-filter
potential temperature flux is reformulated using the Monin-Obukhov similarity
law as
\begin{equation}
(\tau_{\theta z})_0 = \left ( \frac{u_{\tau} \kappa}{ \phi_h} \right ) \frac{S_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{S_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{S_1} },
\end{equation}
where $\phi_h$ is the non-dimensional potential temperature gradient from
Monin-Obukhov similarity law~\cite{Etling1996}.
